Hierarchical Phrase-Based Grammar Extraction in Joshua

### 2009-12-14 papers/mt_marathon10_SuffixArray/paper.tex
Added caption
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1242 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\begin{figure}
\begin{algorithmic}[1]
\Function{Compare\_Elements}{$index1$,  $index2$, $max$, $corpusEnd$}
	\For {$i=0$; $i<max$; $i++$}
		\If {$index1+i < corpusEnd$ and $index2+i > corpusEnd$}
			\State \Return{$1$}
		\ElsIf {$index2+i < corpusEnd$ and $index1+i>corpusEnd$}
			\State \Return{$-1$}
		\ElsIf {$corpus[index1+i]$ is lexicographically < $corpus[index2+i]$}
			\State \Return {$-1$}
		\ElsIf {$corpus[index1+i]$ is lexicographically > $corpus[index2+i]$}
			\State \Return {$1$}
		\EndIf
	\EndFor
	\State \Return {$0$}
\EndFunction
\end{algorithmic}
\caption{}
\label{sort}
\end{figure}

@@

It is often useful (especially during MERT) to extract a test set specific grammar once in a preprocessing step, since that test set will be translated many times and re-extracting the grammar each time would be wasteful. The {\tt joshua.prefix\_tree.ExtractRules} program performs this task. When run directly, this program accepts either three arguments (a compiled {\tt .josh} directory, file name for grammar to extract, and test file) or five arguments (source corpus text file, target corpus text file, word alignments text file, file name for grammar to extract, and test file). 
%This program can also be accessed as an Apache Ant task (see Figure \ref{ant-file}). 
The following subsections document the mandatory and optional parameters that can be passed to this program through the {\tt extractRules} ant task.

>>>>

\begin{figure}
\begin{algorithmic}[1]
\Function{Compare\_Elements}{$index1$,  $index2$, $max$, $corpusEnd$}
	\For {$i=0$; $i<max$; $i++$}
		\If {$index1+i < corpusEnd$ and $index2+i > corpusEnd$}
			\State \Return{$1$}
		\ElsIf {$index2+i < corpusEnd$ and $index1+i>corpusEnd$}
			\State \Return{$-1$}
		\ElsIf {$corpus[index1+i]$ is lexicographically < $corpus[index2+i]$}
			\State \Return {$-1$}
		\ElsIf {$corpus[index1+i]$ is lexicographically > $corpus[index2+i]$}
			\State \Return {$1$}
		\EndIf
	\EndFor
	\State \Return {$0$}
\EndFunction
\end{algorithmic}
\caption{During suffix array creation, the contents of a corpus array are sorted using the element comparison function {\sc {Compare\_Elements}}}
\label{sort}
\end{figure}

@@

It is often useful (especially during MERT) to extract a test set specific grammar once in a preprocessing step, since that test set will be translated many times and re-extracting the grammar each time would be wasteful. To perform this task, the program {\tt joshua.prefix\_tree.ExtractRules} can be used. When run directly, this program accepts either three arguments (a compiled {\tt .josh} directory, file name for grammar to extract, and test file) or five arguments (source corpus text file, target corpus text file, word alignments text file, file name for grammar to extract, and test file). 
%This program can also be accessed as an Apache Ant task (see Figure \ref{ant-file}). 
The following subsections document the mandatory and optional parameters that can be passed to this program through the {\tt extractRules} ant task.
